A Constructive Ordered Predicate Logic for Category Theory

### 2022-10-13 paper/paper.tex
add some cites

Our work in this paper fits broadly into a line of work on
\emph{directed dependent type theories}, a type theory where the
identity type is interpreted as morphisms in a (possibly
$\infty$-)category.  In directed type theories based on a bisimplicial
model~\cite{riehl-shulman,weinberger,otherweinbegerpaper,licataweaver},
morphism types are defined using an interval object, like in cubical
type theory~\cite{bch,cchm,afh,abcfhl}, and universal properties like
``morphism induction'' are an internally definable property of certain
types.  Other type theories~\cite{north,ahrensnorth} define morphism
types via an induction principle, corresponding to the lifting
properties of certain kinds of fibrations of categories.  While these
previous works can express some constructions on $\Cat$ that are not
expressible in \vett{}, because \vett{} is more restricted, \vett{}
contrariwise has more models, for instance categories enriched in
non-cartesian monoidal categories, so the theorems that are provable
in \vett{} apply in more settings.

>>>>

Our work in this paper fits broadly into a line of work on
\emph{directed dependent type theories}, a type theory where the
identity type is interpreted as morphisms in a (possibly
$\infty$-)category.  In directed type theories based on a bisimplicial
model~\cite{riehlshulman17directed,buchholtzweinberger21fibered,weinberger22thesis,WeaverLicata20},
morphism types are defined using an interval object, like in cubical
type
theory~\cite{bch18,cchm18cubical,angiuli+18cartesian-csl,abcfhl17cartesian},
and universal properties like ``morphism induction'' are an internally
definable property of certain types.  Other type
theories~\cite{north,ahrensnorth} define morphism types via an induction
principle, corresponding to the lifting properties of certain kinds of
fibrations of categories.  While these previous works can express some
constructions on $\Cat$ that are not expressible in \vett{}, because
\vett{} is more restricted, \vett{} contrariwise has more models, for
instance categories enriched in non-cartesian monoidal categories, so
the theorems that are provable in \vett{} apply in more settings.
